### 2020-01-16 nlp_models.tex
NLP tables added...debugging needed

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
 GPT2 (small) & & & & & \\
 GPT2-medium & & & & & \\
 GPT2-large & & & & & \\
 GPT2-xl & & & & &\\

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
GT2 small & 50 & 2.05 & 2.59& 9.78 & 10.03 \\
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 &1.9 2& 7.17 & 7.51 \\

SOMETHING IS WRONG HERE...SOME OUTLIERS OR WE NEED TO FIX THE NORMALIZATION
